\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-10-31 R/create_figures.Rmd
dont try to make the workflow diagram
knits on laptop now

library(here)
library(readr)
library(dplyr)
library(sf)
library(ggplot2)
library(ggthemes)
library(spData)
library(tidyverse)
library(mapview)
library(RColorBrewer)
library(ggspatial)
library(rnaturalearth)
library(rnaturalearthdata)
```

@@

# load and transform additional geospatial data for mapping 
data("us_states", package = "spData")
us_states_2163 <- st_transform(spData::us_states, crs = 2163)
#world_2163 <- st_transform(spData::world, crs = 2163)
world_2163 <- ne_countries(scale = "medium", returnclass = "sf") %>% st_transform(crs = 2163)

# set color palette for NEON domains 
colourCount = length(unique(domains_filtered_2163$DomainID))
getPalette = colorRampPalette(brewer.pal(colourCount, "Spectral"))
colors_domains <- data.frame(names = sort(unique(domains_filtered_2163$DomainName)),
                        values = getPalette(colourCount)) #colorRampPalette
```

```{r make_map, fig.height=4, fig.width=6}
# make the map 
ggplot() + 
  # US States
  geom_sf(data = us_states_2163, fill="grey80", color="gray70", alpha=0.3) + 
  # continent boundaries for context 
  geom_sf(data = world_2163, fill="grey80", color="gray50", alpha=0.5) +
  # NEON domains containing spectra
  geom_sf(data = domains_filtered_2163, aes(fill = factor(DomainName)), 
          alpha = 0.7, color = "gray40") + 
  # fill label in legend 
  labs(fill = "NEON Domain") + 
  # apply fill color scale for neon domains 
  scale_fill_manual(breaks = colors_domains$names, values = colors_domains$values) + 
  # add the other NEON domains, just as outlines + 
  geom_sf(data = domains_all_2163, alpha = 0, color = "gray40") +
  # add NEON spectra locations as points
  geom_sf(data = spectra_2163) + 
  # set the extent based on NEON domains where we have spectral data 
  coord_sf(crs = st_crs(2163),
           expand = FALSE,
           xlim = c(as.numeric(st_bbox(domains_filtered_2163)[1]),    # xmin
                    as.numeric(st_bbox(domains_filtered_2163)[3])),   # xmax 
           ylim = c(as.numeric(st_bbox(domains_filtered_2163)[2]),    # ymin
                    as.numeric(st_bbox(domains_filtered_2163)[4]))) + # ymax
  # add scale bar and north arrow 
  annotation_scale(location = "bl", width_hint = 0.4, style = "bar") +
  # add north arrow
  annotation_north_arrow(location = "bl", which_north = "true", 
                         pad_x = unit(0.15, "in"), pad_y = unit(0.25, "in"),
                         style = north_arrow_fancy_orienteering) +
  # set theme 
  theme_bw() 
```

@@

```{r}
library(DiagrammeR)
library(rsvg)

>>>>

library(here)
library(readr)
library(dplyr)
library(sf)
library(ggplot2)
library(ggthemes)
library(spData)
library(tidyverse)
library(RColorBrewer)
library(ggspatial)
library(rgeos)
library(rnaturalearth)
library(rnaturalearthdata)
```

@@

# load and transform additional geospatial data for mapping 
data("us_states", package = "spData")
us_states_2163 <- sf::st_transform(spData::us_states, crs = 2163)
#world_2163 <- st_transform(spData::world, crs = 2163)
world_2163 <- rnaturalearth::ne_countries(scale = "medium", returnclass = "sf") %>% st_transform(crs = 2163)

# set color palette for NEON domains 
colourCount <- length(unique(domains_filtered_2163$DomainID))

# colorbrewer palette can only be up to 11 colors though
getPalette <- colorRampPalette(brewer.pal(colourCount, "Spectral"))
colors_domains <- data.frame(names = sort(unique(domains_filtered_2163$DomainName)),
                        values = getPalette(colourCount)) #colorRampPalette

# trying to use a non-color brewer palette to get 14
#getPalette <- c(brewer.pal(name="Spectral", n = 8), brewer.pal(name="Spectral", n = colourCount-8))
#colors_domains <- data.frame(names = sort(unique(domains_filtered_2163$DomainName)),
#                        values = getPalette) 
```

```{r make_map, fig.height=4, fig.width=6}
# make the map 
ggplot() + 
  # US States
  geom_sf(data = us_states_2163, fill="grey80", color="gray70", alpha=0.3) + 
  # continent boundaries for context 
  geom_sf(data = world_2163, fill="grey80", color="gray50", alpha=0.5) +
  # NEON domains containing spectra
  geom_sf(data = domains_filtered_2163, aes(fill = factor(DomainName)), 
          alpha = 0.7, color = "gray40") + 
  # fill label in legend 
  labs(fill = "NEON Domain") + 
  # apply fill color scale for neon domains 
  scale_fill_manual(breaks = colors_domains$names, values = colors_domains$values) + 
  # add the other NEON domains, just as outlines + 
  geom_sf(data = domains_all_2163, alpha = 0, color = "gray40") +
  # add NEON spectra locations as points
  geom_sf(data = spectra_2163) + 
  # set the extent based on NEON domains where we have spectral data 
  coord_sf(crs = st_crs(2163),
           expand = FALSE,
           xlim = c(as.numeric(st_bbox(domains_filtered_2163)[1]),    # xmin
                    as.numeric(st_bbox(domains_filtered_2163)[3])),   # xmax 
           ylim = c(as.numeric(st_bbox(domains_filtered_2163)[2]),    # ymin
                    as.numeric(st_bbox(domains_filtered_2163)[4]))) + # ymax
  # add scale bar and north arrow 
  ggspatial::annotation_scale(location = "bl", width_hint = 0.4, style = "bar") +
  # add north arrow
  ggspatial::annotation_north_arrow(location = "bl", which_north = "true", 
                         pad_x = unit(0.15, "in"), pad_y = unit(0.25, "in"),
                         style = north_arrow_fancy_orienteering) +
  # set theme 
  theme_bw() 
```

@@

```{r include=FALSE, eval=FALSE}
library(DiagrammeR)
library(rsvg)

### 2020-10-31 analysis/paper/paper.Rmd
knits on laptop now

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  comment = "#>",
  dpi = 300
)
```

@@

Figure \@ref(fig:fig-spectraExtracted)

@@

Figure \@ref(fig:fig-honestWork)

@@

```{r fig-honestWork, fig.cap = "Caption", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
knitr::include_graphics(here::here("analysis", "figures", "honest_work.jpeg"))
```

@@

```{r fig-spectraExtracted, fig.cap = "Caption", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis", "figures", "spectra_figure_test.png"))
```

>>>>

```{r setup, echo = FALSE}
library(bookdown)
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  comment = "#>",
  dpi = 300
)
```

@@

@@

@@

@@
